%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ---------------------------------------------------------------- 

% Set up the document
\documentclass[a4paper, 11pt, oneside]{Thesis}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn
\graphicspath{{Figures/}}  % Location of the graphics files (set up for graphics to be in PDF format)

% Include any extra LaTeX packages required
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\usepackage{wrapfig}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{urlcolor=blue, colorlinks=true}  % Colours hyperlinks in blue, but this can be distracting if there are many links.

%% ----------------------------------------------------------------
\begin{document}
\frontmatter	  % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title  {Thesis}
\authors  {\texorpdfstring
            {{Junjie Zhang}}
            {Junjie Zhang}
            }
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\subject    {}
\keywords   {}

\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round

% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers

%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here
\Declaration{

\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

I, Junjie Zhang, declare that this thesis titled and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item[\tiny{$\blacksquare$}] This work was done wholly or mainly while in candidature for a research degree at the University of Adelaide.
 
\item[\tiny{$\blacksquare$}] Where any part of this thesis has previously been submitted for a degree or any other qualification at the University  of Adelaide or any other institution, this has been clearly stated.
 
\item[\tiny{$\blacksquare$}] Where I have consulted the published work of others, this is always clearly attributed.
 
\item[\tiny{$\blacksquare$}] Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
 
\item[\tiny{$\blacksquare$}] I have acknowledged all main sources of help.
 
\item[\tiny{$\blacksquare$}] Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.
\\
\end{itemize}
 
 
Signed:\\
\rule[1em]{25em}{0.5pt}  % This prints a line for the signature
 
Date:\\
\rule[1em]{25em}{0.5pt}  % This prints a line to write the date
}
\clearpage  % Declaration ended, now start a new page

% The Abstract Page
% \addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents

\begin{abstract}
   Scene classification is an important field in computer vision. For similar weather condition, there are some obstacles for extracting features from outdoor images. In this thesis, we present a novel approach to classify cloudy and sunny weather. Inspired by recent study of a deep convolutional neural network and the spatial pyramid matching, we generate a model based on the ImageNet dataset. Starting with parameters learned from the other classification task, we fine-tune the model via the outdoor images. Experiment demonstrates that our classifier can achieve the state of the art accuracy.
   
   Multi-label learning is a variant of supervised learning where the task is to learn a set of examples, which can belong to multiple classes. This is a version of popular multi-class classification problems in which each sample has one class label only. It can apply in a wide range of applications, which include text categorisation, semantic image labelling etc.. A lot of research work has been done on multi-label learning with different approaches. In this thesis, I trained a neural network from scratch up based on the generated artificial images. The model is learned by minimising error function based on the Hamming distance, through the backpropagation. The model has high capability of generalisation.
\end{abstract}



\clearpage  % Abstract ended, start a new page
%% ----------------------------------------------------------------

\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

I am grateful to my major supervisor, Prof. Chunhua Shen, and co-supervisor, Senior Lecturer Qinfeng Shi, whose expertise, understanding, and warmly support made it pssible for me to work on the neural network that is of great interest to me. It is a pleasure working with them. Prof. Shen's dedication and keen interest to help his students had been solely and mainly responsible for completing my work. His timely advice, meticulous scrutiny, and scholarly advice have helped me to accomplish the tasks.

I would like to thank for my co-supervisor, Qinfeng Shi, for his time and effort on helping me understand research work and knowledge of machine learning.

I thank PhD candidate Teng Li who cooperated to work on the Weather Classification project. We set up experiment environment, analysed test results and discussed approaches. His prompt inspirations, timely suggestions with kindness, and enthusiasm work attitude have helped to achieve the perfect classification accuracy.

I am extremely thankful to research fellow, Guoshen Lin, for his kind help and discussion about the weather classification and the multi-label classification.

I would also like to thank staffs and visitors in the Australian Center for Visual Technologies (ACVT). Attending the reading group has enriched my knowledge in Computer Vision and learned a lot from them.

Finally, I would like to warmly thank the staffs in the School of Computer Science at the University of Adelaide. Julie Mayo, Sharyn Liersh and Jo Rogers have done excellent jobs on administration which helps students to be focus on their research work.

}
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
\listoftables  % Write out the List of Tables

%% ----------------------------------------------------------------
\setstretch{1.5}  % Set the line spacing to 1.5, this makes the following tables easier to read
\clearpage  % Start a new page
\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
{
% \textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
%\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere \\
\textbf{SVM} & \textbf{S}pport \textbf{V}ector \textbf{M}achine \\
\textbf{ANN} & \textbf{A}rtificial \textbf{N}eural \textbf{N}etwork \\
\textbf{ROI} & \textbf{R}ogin \textbf{o}f \textbf{I}nterest \\
\textbf{SIFT} & \textbf{S}cale \textbf{I}nvariant \textbf{F}eature \textbf{T}ransform \\
\textbf{SGD} & \textbf{S}tochastic \textbf{G}radient \textbf{D}escent \\
\textbf{BP} & \textbf{B}ack\textbf{P}ropagation\\
\textbf{MLE} & \textbf{M}aximum  \textbf{L}ikelihood \textbf{E}stimation \\
\textbf{MAP} & \textbf{M}aximum  \textbf{A} \textbf{P}osteriori \\
\textbf{CNN} & \textbf{C}onvolutional  \textbf{N}eural \textbf{N}etwork \\
\textbf{ReLU} & \textbf{Re}ctified  \textbf{L}inear \textbf{U}nit \\
\textbf{SPM} & \textbf{S}patial  \textbf{P}yramid \textbf{M}atching \\
\textbf{SPP} & \textbf{S}patial  \textbf{P}yramid \textbf{P}ooling \\
\textbf{GPU} & \textbf{G}raphics   \textbf{P}rocessing \textbf{U}nit \\
\textbf{BR} & \textbf{B}inary   \textbf{R}elevance Classifier\\
\textbf{CC} & \textbf{C}lassifier   \textbf{C}hains Classifier\\
\textbf{CML} & \textbf{C}ollective   \textbf{M}ulti-\textbf{L}abel Classifier \\

}

%% ----------------------------------------------------------------
%%\clearpage  % Start a new page
%%\lhead{\emph{Physical Constants}}  % Set the left side page header to "Physical Constants"
%%\listofconstants{lrcl}  % Include a list of Physical Constants (a four column table)
%%{
% Constant Name & Symbol & = & Constant Value (with units) \\
%%Speed of Light & $c$ & $=$ & $2.997\ 924\ 58\times10^{8}\ \mbox{ms}^{-\mbox{s}}$ (exact)\\

%%}

%% ----------------------------------------------------------------
\iffalse
\clearpage  %Start a new page
\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
\listofnomenclature{lll}  % Include a list of Symbols (a three column table)
{
% symbol & name & unit \\
$a$ & distance & m \\
$P$ & power & W (Js$^{-1}$) \\
& & \\ % Gap to separate the Roman symbols from the Greek
$\omega$ & angular frequency & rads$^{-1}$ \\
}
\fi
%% ----------------------------------------------------------------
% End of the pre-able, contents and lists of things
% Begin the Dedication page
%%\setstretch{1.3}  % Return the line spacing back to 1.3

%%\pagestyle{empty}  % Page style needs to be empty for this page
%%\dedicatory{For/Dedicated to/To my\ldots}

%%\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics

%% ----------------------------------------------------------------
%% Weather Classification

\clearpage
\part{Weather Classification}
\maketitle

%% ----------------------------------------------------------------
\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{fancy}  % Return the page headers back to the "fancy" style

% Include the chapters of the thesis, as separate files
% Just uncomment the lines as you write the chapters
\input{./Chapters/Chapter1} % Introduction

\input{./Chapters/Chapter2} % Background Theory and Related Work

\input{./Chapters/Chapter3} % Methodology

\input{./Chapters/Chapter4} % Experiment 1

\clearpage
\part{Multilabel Learning}
\maketitle

\input{./Chapters/Chapter5} % Multilabel Introduction

\input{./Chapters/Chapter6} % Multilabel Background

\input{./Chapters/Chapter7} % Multilabel Methodology

\input{./Chapters/Chapter8} % Multilabel Experiment
%\input{./Chapters/Chapter7} % Conclusion

%% ----------------------------------------------------------------
% Now begin the Appendices, including them as separate files

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

\appendix % Cue to tell LaTeX that the following 'chapters' are Appendices

%\input{./Appendices/AppendixA}	% Appendix Title

%\input{./Appendices/AppendixB} % Appendix Title

%\input{./Appendices/AppendixC} % Appendix Title

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
\backmatter

%% ----------------------------------------------------------------
\label{Bibliography}
\lhead{\emph{Bibliography}}  % Change the left side page header to "Bibliography"
\bibliographystyle{unsrtnat}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\bibliography{Bibliography}  % The references (bibliography) information are stored in the file named "Bibliography.bib"

\end{document}  % The End
%% ----------------------------------------------------------------